# Generating data {#generating}

We start by defining functions that we can use to generate a design matrix with two kinds of groups of variables, which we call cluster structures and complex dependencies.

## Cluster structure

Here, we generate $s$ clusters of features, each with $d$ features.  A cluster consists of a representative variable $X_k\sim N_n(0, I_n)$ and $d-1$ proxy variables $X_j=X_k+\delta_j$, with $\delta_j\sim N_n(0,\eta^2 I_n)$.

```{r}
#' Generate cluster design matrix
#' 
#' A function that generates a design matrix with cluster structures. 
#' The representative feature follows N(0,1), and perturbation direction follows
#'  N(0, eta^2).
#' 
#' @param n sample size
#' @param s number of clusters
#' @param d number of features in each cluster
#' @param eta standard deviation of the perturbation direction
#' 
#' @return an n by s*d matrix
#' 
#' @export
gen_clust <- function(n, s, d, eta = 0.1) {
  X = matrix(stats::rnorm(n*s*d), nrow = n)
  
  id_rep = (1:s) * d - (d-1)
  id_prox = setdiff(1:ncol(X), id_rep)
  track_rep = 0
  for(i in 1:ncol(X)) {
    if(i %in% id_rep) {
      track_rep = i
    } else {
      X[,i] = X[,track_rep] + stats::rnorm(n, sd = eta)
    }
  }
  return(X)
}
```

We have used a function in the package `stats`, so let's import it.

```{r}
usethis::use_package("stats")
```


This creates `s*d` features, where the first feature of each cluster is the representative feature.  To quickly check this, observe that if we set `eta` to be 1, the variance of the proxy features are all about twice that of the representative feature:

```{r}
testthat::test_that("gen_clust works as expected", {
  set.seed(123)
  Xclust <- gen_clust(n=1000, s=2, d = 4, eta = 1)
  testthat::expect_equal(round(apply(Xclust, 2, var)),
                         c(1, 2, 2, 2, 1, 2, 2, 2))
})
```

## Complex Dependencies Block

The complex dependencies blocks consist of parent-child relationships.  As described in the paper, "the parent features are generated by
$X_j \overset{iid}{\sim} \mathcal{N}(0, I_n)$, $j\in \mathcal{K}_l$, and the child is defined as $X_{c_l} = \sum_{j\in \mathcal{K}_l} X_j + \delta_{c_l}$, where the perturbation directions follow $\delta_{c_l} \overset{iid}{\sim} \mathcal{N}(0, \eta_l^2 I_n)$."

```{r}
#' Generate design matrix with complex dependency
#' 
#' A function that generates a design matrix with complex dependency structures. 
#' The parent features follow N(0,1), and perturbation direction follows N(0, eta^2).
#' 
#' @param n sample size
#' @param nb number of blocks
#' @param b number of parents in each block
#' @param eta standard deviation of the perturbation direction
#' 
#' @return an n by nb*(b+1) matrix
#' 
#' @export
gen_block <- function(n, nb, b, eta = 0.1) {
  X = matrix(stats::rnorm(n*nb*(b+1)), nrow = n)
  id_child = seq(from = b+1, to = nb*(b+1), by = b+1)
  id_parents = setdiff(1:ncol(X), id_child)
  for(i in 1:ncol(X)) {
    if(i %in% id_parents) {
    } else {
      X[,i] = apply(X[,(i-b):(i-1)], 1, sum) + stats::rnorm(n, sd = eta)
    }
  }
  return(X)
}
```

In this function, the child feature is the last of each block. Let's check that we have this correct:

```{r}
testthat::test_that("gen_block works as expected", {
  set.seed(123)
  Xblock <- gen_block(n=1000, nb=2, b = 4, eta = 1)
  testthat::expect_equal(round(apply(Xblock, 2, var)),
                         c(1, 1, 1, 1, 5, 1, 1, 1, 1, 5))
})
```

## Make some example data

With these two functions defined, we can now generate some example data that we'll use to demonstrate the functions defined in the rest of this document.

```{r}
ex <- list(
  n = 300,
  nclust = 2,
  sindep = 5,
  p = 50,
  eta = 0.1
  )
ex$Xclust = gen_clust(ex$n, ex$nclust, d = 2, eta = ex$eta)
ex$Xblock = gen_block(ex$n, nb = 1, b = 2, eta = ex$eta)
ex$Xindep = matrix(stats::rnorm(ex$n * (ex$p - ncol(ex$Xclust) - ncol(ex$Xblock) )),
                   nrow = ex$n)
ex$X = cbind(ex$Xclust, ex$Xblock, ex$Xindep)
ex$beta = c(
  rep(c(1, 0), ex$nclust),
  c(1, -1, 0),
  rep(0, ex$p - ncol(ex$Xclust) - ncol(ex$Xblock))
)
ex$y = ex$X %*% ex$beta + stats::rnorm(ex$n, sd = 1.5)
```


